Formatting Instructions for RLDM

### 2019-02-25 manuscripts/rldm2019/template.tex
reorganization of manuscripts.

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{manuscript,palatino}
\usepackage{graphicx}

\title{something something about anxiety}

\author{
Samuel Zorowitz \\
Princeton Neuroscience Institute\\
Princeton University\\
Princeton, NJ 08540 \\
\texttt{zorowitz@princeton.edu} \\
\And
Nathaniel Daw \\
Princeton Neuroscience Institute\\
Princeton University\\
Princeton, NJ 08540 \\
\texttt{ndaw@princeton.edu} \\
}

@@

\begin{abstract}
To be filled in
\end{abstract}

\keywords{
reinforcement learning; avoidance; anxiety
}

>>>>

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{rldmsubmit,palatino}
\usepackage{graphicx}

\title{Formatting Instructions for RLDM}

\author{
Dorsal S.~Raphe\thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213 \\
\texttt{raphe@cs.cranberry-lemon.edu} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
\And
Coauthor \\
Affiliation \\
Address \\
\texttt{email} \\
(if needed)\\
}

@@

\begin{abstract}
The \emph{title} should be a maximum of 100 characters.

The \emph{abstract} should be a maximum of 2000 characters of text,
including spaces (no figure is allowed). You will be asked to copy
this into a text-only box; and it will appear as such in the
conference booklet. Use 11~point type, with a vertical spacing of
12~points.  The word \textbf{Abstract} must be centered, bold, and in
point size 12. Two line spaces precede the abstract.
\end{abstract}

\keywords{
enter key words here
}

\acknowledgements{We are deeply indebted to Google DeepMind and
the Weinberg Institute for Cognitive Science for
their generous support of RLDM2017.}
